### 2014-02-17 proposal/new_proposal.tex
Minor tweaks and formatting fixes.

In this paper, we focus on department stores. This space is prime for our
analysis since there are a number of competing stores that have overlapping
catalogues. We model the relationships between products with a
\emph{recommendation graph}, which is directed graph between the products in a
catalogue. A directed edge from product A to product B means that if a user
likes product A, he/she is likely to like product B. First we construct the
recommendation graphs of different department stores using the
recommendations given for each product on their websites. With these
original graphs, we aim to add meaningful edges within one retailers graph
(representing a new recommendation) and between different retailer graphs
(representing a candidate to add to a catalogue).

@@

\section*{Methods}
\subsection*{Method 1}
create similarity scores between items. If items are similar, we add edges
in both directions to the recommendation graph. To determine the threshold
of how high the score must be before adding an edge, we calculate the
average similarity between items that are connected in the original graph.
These edges can connect two items in the same catalogue or items across
catalogues.

>>>>

In this paper, we focus on department stores. This space is well suited for our
analysis since there are a number of competing stores with overlapping
catalogues. We model the relationships between products with a
\emph{recommendation graph}, which is a directed graph between the products in
a catalogue. A directed edge from product A to product B means that if a user
likes product A, he/she is likely to like product B. First we construct the
recommendation graphs of different department stores using the recommendations
given for each product on their websites. With these original graphs, we aim to
add meaningful edges within one retailer's graph (representing a new
recommendation) and between different retailer graphs (representing a candidate
to add to a catalogue).

@@

\section*{Methods}
\subsection*{Method 1}
Create similarity scores between items. If items are similar, we add edges in
both directions to the recommendation graph. To determine the threshold of how
high the score must be before adding an edge, we calculate the average
similarity between items that are connected in the original graph.  These edges
can connect two items in the same catalogue or items across catalogues.
